---
title: "Preliminary Results"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE,message=FALSE,warning=FALSE,
                      collapse = TRUE,
                      comment = "#>", 
                      fig.path = "images/fticr_markdown/"
                      )

source("code/0-packages.R")

```

---
 
## FTICR-MS 
```{r}
# load files

data_long = read.csv("data/processed/fticr_data_long.csv", stringsAsFactors = F)
meta_hcoc = read.csv("data/processed/fticr_meta_hcoc.csv", stringsAsFactors = F)
fticr_meta = read.csv("data/processed/fticr_meta.csv", stringsAsFactors = F)

data_hcoc = data_long %>% 
  left_join(meta_hcoc, by = "formula")
```

### Van Krevelen Plots
#### domains

```{r vankrev_domains, fig.height=5, fig.width=5}
meta_hcoc %>% 
  left_join(dplyr::select(fticr_meta, formula, Class), by = "formula") %>% 
  gg_vankrev( aes(x = OC, y = HC, color = Class))+
  scale_color_viridis_d(option = "inferno")+
  theme_kp()+
  theme(legend.text = element_text(size=8))+
  NULL
```

version 2. taken from [Ohno et al. 2018, Geoderma](https://doi.org/10.1016/j.geoderma.2018.04.006)  
using H/C, O/C, and AImod  
```{r vankrev_domains2, fig.height=5, fig.width=5}
meta_hcoc %>% 
   ggplot(aes(x = OC, y = HC)) +
    #geom_point(size=2, alpha = 0.2) + # set size and transparency
    ylab("H/C") +
    xlab("O/C") +
    xlim(0,1.25) +
    ylim(0,2.5) +
   #scale_color_manual(values = pnw_palette("Sailboat",2))+
    geom_segment(x = 0.0, y = 1.5, xend = 1.2, yend = 1.5,color="black",linetype="longdash") +
    geom_segment(x = 0.0, y = 0.7, xend = 1.2, yend = 0.4,color="black",linetype="longdash") +
    geom_segment(x = 0.0, y = 1.06, xend = 1.2, yend = 0.51,color="black",linetype="longdash") +
   
   annotate("text", label = "aliphatic", x = 0.2, y = 1.75)+
   annotate("text", label = "highly unsaturated/ \n lignin-like", x = 0.2, y = 1.25)+
   annotate("text", label = "aromatic", x = 0.2, y = 0.85)+
   annotate("text", label = "condensed aromatic", x = 0.2, y = 0.35)+
   guides(colour = guide_legend(override.aes = list(alpha=1)))+
  theme_kp()
```

#### treatment effect

**peaks detected in 2/4 replicates**   

**initial (pre-conditioned to temp and clay)**

```{r vankrev_initial_2of4, fig.height=7, fig.width=7}

gg_vankrev(data_hcoc %>% filter(Pre_post=="Initial"), aes(x = OC, y = HC, color = Clay))+
  ggtitle("initial")+
  stat_ellipse()+
  facet_grid(Temperature~Moisture)+
  theme_kp()+
  NULL
```

**final**

```{r vankrev_final_2of4, fig.height=7, fig.width=7}
gg_vankrev(data_hcoc %>% 
             filter(Pre_post=="Final"), 
           aes(x = OC, y = HC, color = Clay))+
  geom_point(alpha = 0.1, size=0.1)+
  ggtitle("final")+
  stat_ellipse()+
  facet_grid(Temperature~Moisture)+
  theme_kp()+
  NULL
```

---

### FTICR QC

#### How many times was each peak seen?
If n = 4, the peak was seen in all 4 replicates.  
Usually include only peaks seen all/majority of replicates.  


```{r fticr_qc, fig.width=12, fig.height=7}
gg_vankrev(data_hcoc %>% filter(Pre_post=="Initial"), aes(x = OC, y = HC, color = as.factor(n)))+
  ggtitle("initial")+
  facet_grid(Temperature+Moisture~Clay+n)+
  theme(legend.position = "none")+
  #theme_kp()+
  NULL

gg_vankrev(data_hcoc %>% filter(Pre_post=="Final"), aes(x = OC, y = HC, color = as.factor(n)))+
  ggtitle("final")+
  facet_grid(Temperature+Moisture~Clay+n)+
  theme(legend.position = "none")+
  #theme_kp()+
  NULL

```



----
#### Session Info
date run: `r Sys.Date()`

```{r}
sessionInfo()
```

